Distrivia: A Distributed Trivia Game

### 2011-04-08 papers/phase-one/paper.tex
Add section about NGINX and EC2
Minor grammer edits to phase 1 paper

We use round robin DNS to allow our clients to be completely ignorant of our servers.  Load distributors
can be added and removed from the DNS server and the clients will be completely ignorant of this
and unaffected.  The load sharers in turn know about our data servers and do their best to
distribute the load across them.  When a new server is added, it is just added to our load distributor
configuration file and clients can start using it.  When a server fails, the distributors will stop directing
traffic to it.

We are currently using Riak as our database backend. We chose Riak for multiple
reasons, but the biggest was it's focus on  scalability, fault-tolerance,
availability, and replication. Riak is a Amazon Dynamo \cite{dynamo} inspired
database, it supports full master less replication. In Riak every node can
server client requests and they are propagated to the rest of the cluster.
In our system we have made sure that this replication occurs between nodes
on Amazon EC2's internal Gigabit ethernet so it is as fast as possible. Riak
also has the unique property that if all of the nodes but one fail, the single
node can still accept both reads and writes to the database. When the other
nodes return to operational state from failure, all changes will automatically
be propagated to all of the nodes. This feature is the basis for our ability to
support and recover from partial failures. In the event that two Riak nodes accept
writes from two separate clients modifying the same data and Riak is unable
to resolve the conflict the user is given both versions and allowed to resolve
the conflict them selves. However we have configured our installation so this
can not occur, we have specified that every available node must agree on a
write before it is committed. Given the relatively small number of nodes (five)
that will take part in this agreement, we decided that the possible overhead
was acceptable for the increased level of consistency it gives us.

Our team is taking a very proactive stance towards security. All of our machines are properly fire walled so that
outside clients can not authenticate to our database cluster. Also we have implemented SSL through our entire infrastructure.
Our load balancer's automatically redirect http:// to https:// and once you are in https:// at the load balancer, SSL continues all the
way back to our actual web application back end serving responses over a SSL wrapped socket. This way no passwords are ever
sent in clear text. Our group even found a SSL certificate authority who was willing to sign our SSL certificate for free. This gives
us actual fully functional, authenticate able SSL infrastructure. In order to make sure that our system properly secures user information,
we stuck with the industry standard of storing a hashed version of the users password instead of the password itself. We decided on using
the cryptographically secure hashing function designed for passwords known as bcyrpt \cite{bcrypt}.

>>>>

We use round robin DNS to allow our clients to be completely ignorant of our servers.  Load sharers
can be added and removed from the DNS server and the clients will be completely ignorant of this
and unaffected.  The load sharers in turn know about our data servers and do their best to
distribute the load across them.  When a new server is added, it is just added to our load sharer
configuration file and clients can start using it.  When a server fails, the sharers will stop directing
traffic to it.

We are currently using Riak as our database backend. We chose Riak for multiple
reasons, but the biggest was it's focus on  scalability, fault-tolerance,
availability, and replication. Riak is a Amazon Dynamo \cite{dynamo} inspired
database, it supports full masterless replication. In Riak every node can
serve client requests and they are propagated to the rest of the cluster.
In our system we have made sure that this replication occurs between nodes
on Amazon EC2's internal Gigabit ethernet so it is as fast as possible. Riak
also has the unique property that if all of the nodes but one fail, the single
node can still accept both reads and writes to the database. When the other
nodes return to operational state from failure, all changes will automatically
be propagated to all of the nodes. This feature is the basis for our ability to
support and recover from partial failures. In the event that two Riak nodes accept
writes from two separate clients modifying the same data and Riak is unable
to resolve the conflict the user is given both versions and allowed to resolve
the conflict them selves. However we have configured our installation so this
can not occur, we have specified that every available node must agree on a
write before it is committed. Given the relatively small number of nodes (five)
that will take part in this agreement, we decided that the possible overhead
was acceptable for the increased level of consistency it gives us.

Our team is taking a very proactive stance towards security. All of our machines are properly firewalled so that
outside clients can not authenticate to our database cluster. Also we have implemented SSL through our entire infrastructure.
Our load balancer's automatically redirect http:// to https:// and once you are in https:// at the load balancer, SSL continues all the
way back to our actual web application back end serving responses over a SSL wrapped socket. This way no passwords are ever
sent in clear text. Our group even found a SSL certificate authority who was willing to sign our SSL certificate for free. This gives
us actual fully functional, authenticatable SSL infrastructure. In order to make sure that our system properly secures user information,
we stuck with the industry standard of storing a hashed version of the users password instead of the password itself. We decided on using
the cryptographically secure hashing function designed for passwords known as bcyrpt \cite{bcrypt}.
